Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-18 paper/paper.tex
Add some todos in the paper
Include another contribution in the introduction and add research questions
Refactor

In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
questions in this paper (Section \ref{correlations}):

This study brings several contributions to the research community:
\begin{itemize}
  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000) spanning
  across 38 different projects;
  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
\end{itemize}

@@

Strengthening the argument that readability matters considerably in bug report 
quality is the work of Hooimeijer et. al \cite{hooimeijer2007modeling}. They ran an analysis over
27000 bug reports from the Mozilla Firefox project, looking at self-reported 
severity, readability, daily load, submitter reputation and changes over time. 
After running the evaluation, they not only found out about the importance of
readability in bug reports, but also that attachment and comment counts are 
valuable for faster triaging and that patch count, for example, does not
contribute in the same manner as the previous two.

Another research that agrees that stack traces are helpful in solving bug
reports faster is the one performed by Schroter et. al \cite{schroter2010stack}. They conducted
the whole experiment on the Eclipse project. They first extracted the stack
traces using the infoZilla tool(\cite{bettenburg2008extracting}), followed by
linking the stack traces to changes in the source code (change logs) by mining
the version repository of the Eclipse project. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame, with 40\% being fixed in exactly the first
stack frame.

Other interesting findings regarding the quality of a software project's tickets
are the ones elicited in \cite{bettenburg2008duplicate}. The authors examined
whether duplicate bug reports are actually harmful to a project or they add 
quality. They collected big amount of data from the Eclipse project and ran
various kind of textual and statistical analysis on the data to find answers.
They reached the conclusion that bug duplicates contain information that is not
present in the master reports. This additional data can be helpful for developers
and it can also aid automated triaging techniques.

@@

One other type of information that could be extracted and used for valuable
purposes is the summary of a bug report, as shown in the work of 
Rastkar et. al \cite{rastkar2010summarizing}. The authors wanted to determine if bug reports
could be summarized effectively and automatically so that developers would
need only analyze summaries instead of full tickets. Firstly, they asked
university students to volunteer to annotate the bug reports collected from
various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
a summary of maximum 250 words in their own sentences. These human-produced 
annotations were then used by algorithms to learn how to effectively summarize a 
bug report.  Afterwards, the authors asked the end users of these bug reports, the 
software developers, to rate the summaries against the original bug reports.
They eventually learned that existing conversation-based extractive summary
generators trained on bug reports produce the best results.

@@

% \begin{table}
% \begin{tabular}{l||c||p{2cm}}
% \emph{Operating System} & \emph{Version} & \emph{Verdict} \\ \hline \hline
% Ubuntu & 12.04 & Everyone's favourite Linux, unless you grew up with
% RedHat \\ \hline
% Slackware & xxx & Pseudo-hacker's Linux, how often do you recompile
% your kernel? \\ \hline
% Mac OS & 10.7 & For people with more money than sense \\ \hline
% \end{tabular}
% \caption{\label{tab-eg}Single column table of figures}
% \end{table}

% \begin{figure}
% \begin{center}
% \includegraphics[scale=0.32]{images/alice.pdf}
% \end{center}
% \caption{\label{fig-eg}An example figure stretching over two columns}
% \end{figure*}

>>>>

In order to provide answers to what factors influence quality in a software ticket, we answer the following seven research 
questions in this paper (Section \ref{correlations}):
\begin{itemize}
  \item does the presence of attachments and their type (e.g. code snippet, screenshot) influence the \emph{Time-To-Close} for 
  a ticket?
  \item does the presence of stack traces improve the ticket quality?
  \item does the presence of steps to reproduce reduce the \emph{Time-To-Close}?
  \item is there a relationship between the number of comments influence \emph{Time-To-Close}?
  \item is there a relationship between 
\end{itemize}

This study brings several contributions to the research community:
\begin{itemize}
  \item an innovative tool was built for the purpose of this project, its strengths lying in its simplicity, speed and
  extensability;
  \item it is one of the few studies in the field that performs a quantitative analysis rather than a qualitative one;
  \item it is one of the very few research projects that investigates such a large number of tickets (over 300,000)
  extracted from 38 different projects;
  \item it is, to our knowledge, the first study to conduct sentiment and grammar correctness analyses on software tickets.
\end{itemize}

@@

%TODO: modify here
Strengthening the argument that readability matters considerably in bug report 
quality is the work of Hooimeijer et. al \cite{hooimeijer2007modeling}. They ran an analysis over
27000 bug reports from the Mozilla Firefox project, looking at self-reported 
severity, readability, daily load, submitter reputation and changes over time. 
After running the evaluation, they not only found out about the importance of
readability in bug reports, but also that attachment and comment counts are 
valuable for faster triaging and that patch count, for example, does not
contribute in the same manner as the previous two.

%TODO: modify here
Another research that agrees that stack traces are helpful in solving bug
reports faster is the one performed by Schroter et. al \cite{schroter2010stack}. They conducted
the whole experiment on the Eclipse project. They first extracted the stack
traces using the infoZilla tool(\cite{bettenburg2008extracting}), followed by
linking the stack traces to changes in the source code (change logs) by mining
the version repository of the Eclipse project. The results showed that 
around 60\% of the bugs that contained stack traces in their reports were fixed
in one of the methods in the frame, with 40\% being fixed in exactly the first
stack frame.

%TODO: modify here
Other interesting findings regarding the quality of a software project's tickets
are the ones elicited in \cite{bettenburg2008duplicate}. The authors examined
whether duplicate bug reports are actually harmful to a project or they add 
quality. They collected big amount of data from the Eclipse project and ran
various kind of textual and statistical analysis on the data to find answers.
They reached the conclusion that bug duplicates contain information that is not
present in the master reports. This additional data can be helpful for developers
and it can also aid automated triaging techniques.

@@

%TODO: modify here
One other type of information that could be extracted and used for valuable
purposes is the summary of a bug report, as shown in the work of 
Rastkar et. al \cite{rastkar2010summarizing}. The authors wanted to determine if bug reports
could be summarized effectively and automatically so that developers would
need only analyze summaries instead of full tickets. Firstly, they asked
university students to volunteer to annotate the bug reports collected from
various open sources projects (i.e. Eclipse, Mozilla, Gnome, KDE) by writing
a summary of maximum 250 words in their own sentences. These human-produced 
annotations were then used by algorithms to learn how to effectively summarize a 
bug report.  Afterwards, the authors asked the end users of these bug reports, the 
software developers, to rate the summaries against the original bug reports.
They eventually learned that existing conversation-based extractive summary
generators trained on bug reports produce the best results.

@@
